---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# numvert

The goal of numvert is to help transform numeric vectors. Regardless of the operation, numvert functions take a numeric vector and return a numeric vector of the same length.

## Installation

You can install numvert from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("drsimonj/numvert")
```

## Example

This example shows you how to conduct common rescaling operations with numvert:

```{r example}
# Create a normally distributed variable with a mean of 25 and SD of 5
x <- rnorm(1000, mean = 25, sd = 5)
hist(x)
```

Use numvert to standardise or normalise it:

```{r}
library(numvert)
```

```{r}
# Normalise between 0 and 1
x_norm <- normalise(x)
hist(x_norm)
```

```{r}
# Standardise to have mean of 0 and SD of 1
x_std <- standardise(x)
hist(x_std)
```

Pro tip: British and American spellings are supported (e.g., `normalize` and `normalise`)
